### 2023-09-15 paper/FPF-WG1.tex
bib
Update FPF-WG1.tex

\vspace{-2.0cm}
\begin{flushright}
Nikhef-2023-009, CERN-TH-2023-165\\
\end{flushright}
\vspace{0.6cm}

@@

Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
in the forward (beam) direction, characterised by energies of up to several TeV.
%
The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
signals that this hitherto ignored particle beam is now available for scientific inquiry.
%
Here we quantify the impact that neutrino deep-inelastic scattering (DIS) structure function
measurements at the LHC would have
on the parton distributions (PDFs) of protons and heavy nuclei.
%
We generate projections for DIS structure functions
at FASER$\nu$ and SND@LHC,
as well as at the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC (HL-LHC).
%
These measurements are found to cover a kinematic region in $x$ and $Q^2$ comparable to that
of the upcoming Electron-Ion Collider, with sub-percent statistical uncertainties
in the FPF case.
%
Including these DIS projections into global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
 and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
 for strangeness and the up and down valence PDFs.
 %
 We show that LHC neutrino data enables improved theoretical
 predictions for core processes at the HL-LHC, such as Higgs and weak gauge
 boson production.
%
 Our analysis demonstrates that exploiting the LHC neutrino beam effectively
 provides CERN with a ``Neutrino-Ion Collider''
 without  requiring modifications in its accelerator infrastructure

@@

\bibliographystyle{utphys}
\bibliography{FPF-WG1}

>>>>

\vspace{-2.0cm}
\begin{flushright}
Nikhef-2023-009 \\ CERN-TH-2023-165\\
\end{flushright}
\vspace{0.6cm}

@@

Proton-proton collisions at the LHC generate a high-intensity collimated beam of neutrinos
in the forward (beam) direction, characterised by energies of up to several TeV.
%
The recent  observation of LHC neutrinos by FASER$\nu$ and SND@LHC
signals that this hitherto ignored particle beam is now available for scientific inquiry.
%
Here we quantify the impact that neutrino deep-inelastic scattering (DIS)
measurements at the LHC would have
on the parton distributions (PDFs) of protons and heavy nuclei.
%
We generate projections for DIS structure functions
for FASER$\nu$ and SND@LHC at Run III,
as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
Forward Physics Facility (FPF) operating concurrently with the High-Luminosity LHC (HL-LHC).
%
We determine that up to one million electron- and muon-neutrino DIS interactions
within detector acceptance can be expected by the end of the HL-LHC,
covering a kinematic region in $x$ and $Q^2$ overlapping with that
of the Electron-Ion Collider.
%
Including these DIS projections into
global (n)PDF analyses, specifically PDF4LHC21, NNPDF4.0,
and EPPS21,  reveals a significant reduction of PDF uncertainties, in particular
for strangeness and the up and down valence PDFs.
%
We show that LHC neutrino data enables improved theoretical
predictions for core processes at the HL-LHC, such as Higgs and weak gauge
boson production.
%
Our analysis demonstrates that exploiting the LHC neutrino beam effectively
provides CERN with a ``Neutrino-Ion Collider''
without  requiring modifications in its accelerator infrastructure.

@@

\bibliographystyle{utphys}
%\bibliography{FPF-WG1}
\input{FPF-WG1.bbl}
